\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm} LFEUI - Investigation Proposal \\ \vspace{4mm} {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-1mm}

### 2023-12-02 text/proposta/prop.tex
Proposal Update

The formula this website uses to compute the energies is the one on the book \cite{krane1988}.

@@

The experimental set-up consists of a Tandem accelerator, a beam line with an electromagnet and a chamber with both the samples and the detectors.
The accelerator produces a beam of protons with a kinetic energy of up to 5 MeV which is deviated by the electromagnet and hits the sample. 
The electromagnets deflect particles with different angles according to their charge-to-mass ratio and by that allow us to remove any unwanted particles from the beam and only let the protons pass through.
The detectors used are silicon detectors - these detect charged particles through the ionization they produce in the silicon.

In addition, their are connected to a electronic system that amplifies the signal and sends it to a computer where we
can see the results.

@@

The following diagram shows the experimental set-up:

@@

During the experiments, the accelerator will be producing a beam of protons with a kinetic energy of up to 5 MeV. Because of this there will be a high radiation level near the accelerator.
There are radiation maps that show the radiation levels in different areas of the laboratory.

@@

We will obtain the energy spectrum of the alpha particles resulting from the reaction between the protons and the
samples. 
For the glass samples, we expect to see a profile due to the particles that come from different depths of the sample and
therefore have lost different amounts of energy. In the implant samples, we expect to see a peak at the energy corresponding
to the energy of the alpha particles produced by the reaction.
In both cases, the samples is composed by other types of atoms such as silicon and boron, which will also emit charged
particles.

>>>>

The formula this website uses to compute the energies is on the page 382 of the book \cite{krane1988}.

@@

The experimental set-up consists of a Tandem accelerator, a beam line with an electromagnet and a chamber with both the samples and the detectors.
The accelerator produces a beam of protons with a kinetic energy of up to 5 MeV which is deviated by the electromagnet and hits the sample. 
The electromagnets deflect particles with different angles according to their charge-to-mass ratio and, with that, allows us to remove any unwanted particles from the beam and only let the protons pass through.
The detectors used are silicon detectors - these detect charged particles through the ionization they produce in the silicon.

In addition, they are connected to a electronic system that amplifies the signal and sends it to a computer where we
can see the results.

@@

The following diagram shows the experimental set-up:
Note: We use a tandem accelerator, so the image should have 2 tubes inside the accelerator.

@@

During the experiments, the accelerator will be producing a beam of protons with a kinetic energy of up to 5 MeV. Because of this there will be a high radiation level near the accelerator.
There are radiation maps that show the radiation levels in different areas of the laboratory and need to be strictly followed.

@@

We will obtain the energy spectrum of the alpha particles resulting from the reaction between the protons and the
samples. 
For the glass samples, we expect to see a profile due to the particles that come from different depths of the sample and
therefore have lost different amounts of energy. In the implant samples, we expect to see a peak at the energy corresponding
to the energy of the alpha particles produced by the reaction.
In both cases, the samples are composed by other types of atoms such as silicon and boron, which will also emit charged
particles. By obtaining the expected energy spectrums we can infer the presence of Li in the samples. If possible we will also try
to quantify the amount of Li present by analysing the amout of energy deposited in the spectrums.
